\label{sec:Introduction}

In the realm of network science and graph theory, the identification of cohesive substructures within complex networks is a fundamental task with far-reaching implications. One such critical concept is the k-core of a graph, a mathematical construct that characterizes the inherent structure and resilience of a network. K-cores offer valuable insights into the core-periphery organization of networks and have applications in various fields, including social network analysis, biology, transportation systems, and more.

The k-core of a graph represents a maximal subgraph where every vertex is connected to at least k other vertices within the subgraph. This concept is essential for understanding the robustness and functionality of real-world networks. As the value of k increases, the resulting k-core becomes progressively denser, unveiling the inner layers of a network's connectivity.

The process of identifying k-cores is not a trivial one, and researchers have developed multiple algorithms to efficiently compute them. These algorithms serve as the cornerstone for uncovering the intricate hierarchical structure within networks and have significant implications for various network-related applications.

This report embarks on a comparative study of two distinct algorithms for finding k-cores within a given graph. Our primary objective is to explore and evaluate the strengths and weaknesses of these algorithms in terms of computational efficiency, accuracy, and scalability. By doing so, we aim to provide valuable insights into the selection of an appropriate algorithm based on specific network characteristics and research objectives.

The two algorithms under consideration, which will be thoroughly analyzed and compared in this report, are the \textit{Degree Pruning Algorithm} and an algorithm that uses \textit{DFS} to solve the problem. Both algorithms have gained recognition in the field of network science and have shown promise in identifying k-cores effectively. However, they employ different strategies and heuristics, which may lead to variations in their performance under different network scenarios.

In the subsequent sections of this report, we will delve into the theoretical foundations of k-cores, provide an in-depth explanation of the chosen algorithms, present our experimental methodology, and report the findings of our comparative analysis. By the conclusion of this study, readers will have a comprehensive understanding of the intricacies involved in identifying k-cores and will be equipped with insights to make informed decisions about the choice of algorithm for their specific network analysis tasks.

In the realm of network analysis and graph theory, the \textbf{K-Cores Problem} stands as a fundamental concept, offering valuable insights into the structural characteristics of complex systems. At its core, the K-Cores Problem revolves around identifying cohesive substructures within a graph, shedding light on the inherent organization and robustness of networks.

The K-Cores Problem involves finding the maximal subgraph in which every vertex has a degree of at least \(k\). In simpler terms, it seeks to unveil clusters of nodes that are tightly interconnected, each having a minimum degree threshold \(k\). These subgraphs, known as K-Cores, help us comprehend the intricate relationships and dependencies in various real-world networks.

In the realm of social networks, identifying K-Cores can unveil tightly-knit communities of individuals. These communities might represent closely bonded friend groups, professional circles, or online forums. Analyzing K-Cores aids in understanding the underlying social structures and influential nodes within a network.

In biological research, the K-Cores Problem finds applications in understanding protein-protein interaction networks. Identifying K-Cores helps researchers pinpoint essential proteins in biological pathways, offering crucial insights into diseases and potential drug targets.

When applied to the internet and web graphs, K-Cores shed light on the robustness and connectivity patterns of websites. Websites forming a K-Core represent critical hubs in the web, indicating essential pages and content repositories.

In transportation networks, K-Cores can identify vital junctions or nodes in road systems or public transportation networks. Understanding these K-Cores is pivotal for urban planning, optimizing traffic flow, and ensuring the resilience of transportation infrastructures.

The K-Cores Problem serves as a powerful analytical tool, enabling us to dissect intricate networks into comprehensible substructures. By identifying and studying these cohesive K-Cores, researchers and analysts can gain profound insights into various real-world systems, leading to better decision-making, enhanced network design, and improved overall efficiency in diverse domains.